Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2020-05-07 manuscript/manuscript.tex
updated figs/ ms

>>>>

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/gss-covs-sampleN.pdf}

  \caption{Temporal covariance $\cov(\Delta p_5, \Delta p_t)$, where $t$ varies
  along the x-axis, for a sudden optima shift of 1, for varying replicate
population sizes. The reference time point is the first generation of
selection; dark gray points are the temporal covariance after selection began,
and the light gray points are before.}

  \label{suppfig:gss-covs-sampleN}
\end{figure}
